Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-24 ICLR25/formula.tex
section 4

In the case $W_{az}<0$, to maximize $z$, the LP engine sets $\sol(\hat{a})$ to its minimal value, which is $\sol(\hat{a})=\ReLU(a)$ thanks to Proposition \ref{LP}. In this case, we have $\Utility\_\max^z(a)=0$.
Thus, we have $\Utility\_\max^z(a) \geq 0$ in all cases
as $\sol(\hat{a}) \geq \ReLU(a)$. 
We will show with a more general definition that $0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$ in Prop.~\ref{prop2}. Thus, $\Utility\_\max^z(a)$ can be used to approximate $\Improve\_\max^z(a)$. In particular, for all nodes $a$ with $W_{az}< 0$,
this node will have the smallest $\Utility\_\max\nolimits^z(a)=0$ (thus will not get picked in the open nodes $X$), and indeed it is not having any impact on  $\Sol\_\max_{\{a\}}^z(z)$. This is one stricking difference (but not the only one) with choosing utility based on 
$|W_{az}|$ \cite{DivideAndSlide}.

>>>>

In the case $W_{az}<0$, to maximize $z$, the LP engine sets $\sol(\hat{a})$ to its minimal value, which is $\sol(\hat{a})=\ReLU(\sol(a))$ thanks to Prop.~\ref{LP}. In this case, we have $\Utility\_\max^z(a)=0$.
Thus, we have $\Utility\_\max^z(a) \geq 0$ in all cases
as $\sol(\hat{a}) \geq \ReLU(\sol(a))$ by Prop.~\ref{LP}. 
We will show with a more general definition that $0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$ in Prop.~\ref{prop2}. Thus, $\Utility\_\max^z(a)$ can be used to approximate $\Improve\_\max^z(a)$. In particular, for all nodes $a$ with $W_{az}< 0$,
this node will have the smallest $\Utility\_\max\nolimits^z(a)=0$ (thus will not get picked in the open nodes $X$), and indeed it is not having any impact on  $\Sol\_\max_{\{a\}}^z(z)$. This is one stricking difference (but not the only one) with choosing utility based on 
$|W_{az}|$ \cite{DivideAndSlide}.
